Lock-free Skiplist-based Priority Queues \\ Student Paper for Seminar in Algorithms 2013W \\ Technical University of Vienna

### 2014-02-19 paper/paper.tex
More information in paper title
Further notes

\title{Lock-free skiplist-based priority queues}
\author{Jakob Gruber, 0203440}

@@

\section{Introduction}
\section{Related Work}
\section{Conclusion}

>>>>

\title{Lock-free Skiplist-based Priority Queues \\
       Student Paper for Seminar in Algorithms 2013W \\
       Technical University of Vienna}
\author{Jakob Gruber, 0203440}

@@

\section{Introduction}

\begin{comment}
Sections / rough structure:
* Basic concepts and definitions. Linearizability, sequ./quiescent consistency,
  lock-free, wait-free, disjoint-access parallelism (one of the papers has good
  summaries of these).
  Maybe atomic primitives such as CAS (but probably not).
* Priority queue definitions, semantics, usages. Mention inherent
  non-scalability through DeleteMin().
* Skiplist, heap definitions, semantics, usages.
* Follow development of current state of the art from Hunt Heap ~> Shavit ~>
  Tsigas ~> Linden.
* Maybe benchmarks on mars.
\end{comment}

\section{Related Work}

\begin{comment}
  * hunt: most efficient old-school algorithm
  * lots of other older references in [4]
  * israeli, rappoport: wait-free, non-available atomic primitive
  * lotan, shavit [4]: skiplist, lock-based. first to propose usage of skip-lists [11]
  * sundell, tsigas [3]: skiplist, lock-free, linearizable, unique priorities
  * herlihy, shavit in art of multiprocessor programming: based on [4], lock-free.
  * linden, jonsson [11]: skiplist, lock-free, linearizable, reduced mem contention.
    first lock-free PQ algorithm [11, 12]
  * specialized versions such as
    * bounded priorities: [7] and others
    * probabilistic extractMin, extractMany: [9]
\end{comment}

\section{Conclusion}

\begin{comment}
http://leo.stcloudstate.edu/acadwrite/conclude.html
http://writingcenter.unc.edu/handouts/conclusions/
http://www.wikihow.com/Write-a-Conclusion-for-a-Research-Paper
\end{comment}
